%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[14pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Ryan}{Johnson}
\position{Data Scientist{\enskip\cdotp\enskip}Analytics}
\address{Seattle, WA 98119}

\mobile{+1 (253) 315-0389}
\email{rtjohnson1206@gmail.com}
% \homepage{www.posquit0.com}
% \github{rtjohnson12}
% \linkedin{rtjohnson12}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``I may not have gone where I intended to go, but I think I have ended up where I needed to be."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Climate Corporation Recruitment Team}
  {The Climate Corporation\\710 2nd Ave Suite \#1100\\Seattle, WA 98104}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Data Scientist\\}
% How the letter is opened
\letteropening{To whom it may concern,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Résumé}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {}
  {Ryan Johnson~~~·~~~Cover Letter}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

% \lettersection{About Me}

I am writing to express my strong interest in applying for the open Data Scientist position at The Climate Corporation. Since discovering Climate, I have been eagerly learning as much as I can about both the company's work and the unique scientific space it inhabits. I have greatly enjoyed reading articles and posts from Brian Lutz on LinkedIn; I found the article on fungicide recommendation modeling, for example, both gripping and thought-provoking. Discovering Climate has opened up my pre-conceived notions of what data science is and how it can be used. 

In my current role as a data scientist at a utility analytics company called The Energy Authority (TEA), I have been incredibly fortunate to be exposed to data science at so many levels and from so many angles. My most significant project, for example, was the development and deployment of a short-term load forecasting system. Providing 10-day forecasts of electricity consumption every hour for clients across the country enabled me to connect with nearly every part of the organization. From working with Software Engineers to set up reliable feeds for weather data to working with our Portfolio Analysts and Client Service Managers to validate performance and interpret forecast results, the project offered invaluable experience. Using my experience with this project as a springboard, I worked with my manager to develop and present new standards and best practices for model development and deployment, project performance tracking, and version control. 

As the digital age continues to transform our world, I see data science as the critical intersection between the growing mountains of available data and every-day decision makers. It is the data scientist's role then to not only explore and extrapolate that data but to also recontextualize it, providing real-world benefits to end users. From providing local Public Utility Districts with real-time load estimates so they can schedule their power purchases to informing a farmer's decision when and where to apply fungicide to maximize total yield and protect their crop, data science has limitless applications. I want to work at Climate because of how strongly I resonate with the companies mission: to bring the digital revolution to farmers and sustainably increase their productivity. I am confident that my expertise in data science and professional experience would make me a great fit for your team.

Please find attached my résumé, which describes my skills and experience in greater detail. It would be a privilege to discuss this position in more detail, and thank you again for your time and consideration.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
