%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist II} % Job title
    {Chewy} % Organization
    {Bellevue, WA} % Location
    {Jan 2022 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a sophisticated Hierarchical Reconciliation framework to ensure coherency across forecasting granularities, leveraging cutting-edge research and rigorous testing to meet our team's high accuracy and reliability standards.}
        \item {Enhanced the core demand model by integrating promotion features, fine-tuning model accuracy and responsiveness to market trends and promotional impacts, utilizing AWS Sagemaker and Docker for seamless transition between development and deployment.}
        \item {Redesigned unconstrained demand model, leveraging PDP conversion and clickstream data and AWS Glue for scalable and efficient data processing, allowing for more accurate and insightful demand forecasting and reducing out-of-stock MAPE by up to 10\%.}
        \item {Led effort into topic demand forecasting, employing a temporal knowledge graph approach to capture seasonal and thematic trends effectively.}
    \end{cvitems}
    }

  \cventrytwopositions
    {Analytics Intern}
    {The Energy Authority}
    {Bellevue, WA}
    {Summer 2019}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported other analysts in the maintenance and development of production models and error diagnostics.}
        \item {Redesigned several existing web applications and frameworks allowing for faster data retrieval and an integrated system for generating reports for client presentations.}
        \item {Communicated actionable data insights and issues to management to support decision processes, including changes to long-term forecast methodologies resulting in an average of 10-20 hours saved in annual work-hours per client.}
      \end{cvitems}
    }
    {Data Scientist - Analytics}
    {Sep 2019 - Dec 2022}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Revamped Load Forecasting systems for over 30 clients reducing MAPE by 4-10\%, developed more advanced ML models like RNN/CNN and XGBoost with k-fold cross-validation and outlier detection.}
        \item {Overhauled Hydro Forecasting piepline by integrating new API data feeds from NW river system and plant-level generation, achieving a 5\% reduction in system-level MAPE.}
        \item {Lead transition to new CI/CD system for running containerized applications, enabling streamlined deployments and builds from code repositories and establishing new team standards for project version control and production deployment.}
        \item {Worked with Software Engineering team to develop model failsafe system providing forecasts to real-time traders during critical data feed failures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Business Systems Analyst Intern} % Job title
  %   {Equinix} % Organization
  %   {Sunnyvale, CA} % Location
  %   {Summer 2018} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Created and updated IT application runbooks for core applications.}
  %       \item {Built reports and dashboards to measure success and operational efficiency of organizational initiatives.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
