%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Ryan}{Johnson}
\position{Data Scientist{\enskip\cdotp\enskip}Analytics}
\address{Seattle, WA 98119}

\mobile{+1 (253) 315-0389}
\email{rtjohnson1206@gmail.com}
% \homepage{www.posquit0.com}
\github{rtjohnson12}
\linkedin{rtjohnson12}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``I may not have gone where I intended to go, but I think I have ended up where I needed to be."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Climate Corporation Recruitment Team}
  {The Climate Corporation\\710 2nd Ave Suite \#1100\\Seattle, WA 98104}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Data Scientist/Machine Learning Engineer}
% How the letter is opened
\letteropening{Dear Sir/Madam,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Résumé}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {}
  {Ryan Johnson~~~·~~~Cover Letter}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}

I would like to thank you for the opportunity to apply for the open Data Scientist/ML Engineer position at The Climate Corporation. Though I am just beginning my career in Data Science, I believe my personal strengths, interests, and skills align closely with those outlined in the job description.

First and foremost, I find Data Science to be endlessly fascinating. It is a field that is rapidly evolving and absolutely bursting with opportunities to learn, to transform, and to create truly magnificent things. In my current role as a Data Scientist with The Energy Authority, I've been given the unique opportunity to lead efforts to transform and renew many of our forecasting systems, providing clear and actionable insights to our real-time trading teams and other groups throughout the company. I now strongly believe in the power of Data Science as a supporting tool, enabling and empowering the end users rather than replacing.

\lettersection{Why The Climate Corporation?}

In considering the wide variety of job openings here in Seattle, I was absolutely delighted to find this position. While companies like Facebook, Amazon, and Google do incredible things, I don't think I could be truly passionate about my work when there is such a vast distance between me and "the problem". In stark contrast, I find the combination of Data Science and Agriculture incredibly interesting, where one easily sees themselves in their work. The challenge of optimizing irrigation schedules instantly becomes clear and present, transparent in its need and rewarding in its achievement. I would be thrilled and honored to join a team charged with such tasks.

Please find attached my résumé, which describes my skills and experience in greater detail. It would be a privilege to discuss this position in more detail! Thank you again for your time and consideration.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
